### 2023-05-14 doc/Thesis/chapter/061-results-emma.tex
delete unnecessary files and rearange folder structure

%%% T=4
The coefficients of equations (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) show the same pattern 
as equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}): identical signs and factor 100. 
%The choice of basis functions in combination with their coefficient signs seems more plausible
%for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
%$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $\lambda$ increases the two \textit{optimizands}. 
%LAMBDA 
% TCAL ON OPTIMIZANDS
The influence of $T_{cal}$ on the measures of conductance ($\rho$ and $\gamma$) is highly interesting. 
It was expected that 
calcination temperatures under \oc{400} do not suffice to produce compact layers and 
that therefore the resulting layer does not insulate as well. 
%\td{xxx}
\textit{Optimisands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
according to equations~(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) (see also figures~\ref{fig:g-tcal} and \ref{fig:phd-tcal}), 
ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.
% DESCRIBE COEFFICIENTS
Furthermore, the coefficient of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$; interestingly also on $\hat\lambda$ and $\hat{v}_{cal}$.
The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 
but has the extra factor $\lambda$ (range: 4--12), resulting in the products of coefficients and process variables being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$.
It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}). 
This negative correlation could hint a compenzation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
Similarly, signs of coefficients of $\lambda \cdot T_{cal}$ and $h(\lambda -6) \cdot T_{DB}$ correlate negatively in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) and the product of coefficients and input variables are again similar in order of magnitude. 
%It should be doubted, though, that the $layr$ only appears as interaction term 
%together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
%
%It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
%with $T_{cal}$ and $T_{DB}$. 
%From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_{DB}$ and then the rest of the independent variables. 
The process variables $T_{cal}$ and $\lambda$ appear as \gls{bf}s in generation 3 and 4, whereas $v_{cal}$ only appears in generation 3's \gls{rf}s and $T_{DB}$ only in generation 4's \gls{rf}s.
This can hint the importance of these variables in the process. 
%I highly doubt though that the specific interactions proposed by EMMA are indeed meaningful.

%%% MSE
For each generation the \gls{mse} was calculated for which only samples 
from the optimization were used which were available at the time of prediction. 
That means 15, 20, 25 and 30 samples 
%for $t=0$, 15 samples for $t=1$ and 30 sampes for $t=4$ 
were used to calculate \gls{mse}s at $t=1,2,3,4$, respectively (compare with table~\ref{tab:emma-Gb}).
The \gls{mse}s are 64, 158, 54 and 50 for $t=1,2,3,4$, respectively. 
It is interesting that although prediction functions for $t=3$ predicted $v_{cal}$ perfectly, the combined \gls{mse} for $t=4$ is lower. 
The high \gls{mse} at $t=2$ can be explained by the prediction functions being only constant values. 
Apart from the second generation the \gls{mse} decreases  over time, 
which indicates that the algorithm works. 
This decrease in \gls{mse} might be attributed to overfitting, though, since prediction and validation were performed on the same data. 
%The \gls{mse} for each generation was also calculated between predicted values for pre-optimization samples to check for overfitting, 
The \gls{mse} for each generation's prediction function was also calculated for pre-optimization (out-of-sample) samples, which are unseen data. 
The error sank again with each generation (except for the second generation): 102, 118, 58, 50, respectively for $t=1,2,3,4$. 
%This shows 
The decrease of \gls{mse} with out-of-sample data shows that the regularization method 
of the \gls{mars} algorithm in principle works on investigated samples and that decrease of \gls{mse} is not due to overfitting. 
%
%\td{It should be noted, that the validation \gls{mse} for $t=1$ is much higher.}
When compraring the out-of-sample and in-sample \gls{mse}s it can be noted that at $t=1$ the out-of-sample \gls{mse} is close to 1.5 fold of in-sample and at $t=2$ vice versa.
%The high validation \gls{mse} for $t=1$ (nearly 1.5 fold instead of circa 1 fold of \gls{mse}) 
This shows the poor prediction ability at the beginning of the optimization which improved with generations.
This decrease in validation (out-of-sample) \gls{mse} supports the hypothesis stated at the beginning of this section: 
the measure of conductance was underestimated and and the estimate improved over time (see table~\ref{tab:emma-pred-G}).
%\td{why is \gls{mse} higher with higher values? No homoscedasticity ( equality of variance)?
%Or rather \gls{mse} at $t=2$ high because \gls{rf}s at $t=2$ poor and gen=2 samples are chosen with help of \gls{rf} at $t=2$? 
%}

%%% PROBLEMS 
Even though the main \textit{optimizands} were minimized as required, the \gls{rf}s were not satisfactory. 
The two main problems were too many independent variables and too many dependent variables. 
Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
Too many independent variables make it harder to distinguish variance due to random error (e.g. unmeasured and uncontrolled variables) from variance due to dependency. % of chosen dependent variables. 
The difficulty of identifying meaningful correlation is mainly owed to the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
%
%In the here presented optimization model 
%the data points per independent variable 
%(events per predictor variable EPV) are as low as 5. 
The \gls{epv} (data points per independent varible) are as low as 5 in the here presented optimization. % model and data acquisition method
By eliminating three independent variables the \gls{epv} could rise to 10, which is stated 
as rule of thumb for mulitvariate regression\cite{vittinghoff2007relaxing}. 
The results obtained with limited sample number deliver remarkable insightfulness %are quite respectable. 
comparing to an \gls{epv} of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
and an \gls{epv} of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
%In the original \gls{emma} paper\cite{villanova2010function} the \gls{epv} is 20.
%\td{In the original \gls{mars} paper\cite{friedman1991multivariate} the model is said 
%to work well on 20-50 events per predictor varibale.
%In the current model EPV are around 5, which is even low for a conservative 
%rule of thumbs of 10-15 EPV\cite{vittinghoff2007relaxing}.
%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
%Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
%}
%

@@

The two independent variables $v_{cal}$ and $\lambda$ were included as \textit{optimizands} for two reasons: 
Maximizing the calcination velocity and minimizing the number of layer application iterations leads to minimization of process time.
The process time optimization would be better placed in a follow up study. 
The second reason for including independent variables was to check if the model works. 
This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimizands} and thus 
additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables and chose future data points. 
The second flaw is that there are obsiously better methods to assess the quality of a model than to make it more complex. 
%Good alternatives would have been leave-one-out or cross validation.
Validation methods for sparse data include resampling via leave-one-out or $k$-fold cross validation\cite{kartam1997artificial}.

\iffalse
\td{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%\subsection{how did evolve over time?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{rational behind including $v_{cal}$ and $\lambda$ as optimizands}
}
%
%Three major flaws behind this consideration became obvious with time: 
%
\
\td{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations (\ref{eq:emma-G4})? and (\ref{eq:emma-phd4})?).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}

>>>>

%%% T=4
The coefficients of equations (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) show the same pattern 
as equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}): identical signs and factor 100. 
%The choice of basis functions in combination with their coefficient signs seems more plausible
%for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
%$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $\lambda$ increases the two \textit{optimizands}. 
%
% TCAL ON OPTIMIZANDS
The influence of $T_{cal}$ on the measures of conductance ($\rho$ and $\gamma$) is highly interesting. 
It was expected that 
calcination temperatures under \oc{400} do not suffice to produce compact layers and 
that therefore the resulting layer does not insulate as well. 
The original recipe by Hu et al.\cite{Hu2016} used \oc{500} and thus even \oc{400} are low.
\textit{Optimizands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
according to equations~(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) (see also figures~\ref{fig:g-tcal} and \ref{fig:phd-tcal}), 
ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.
%
% DESCRIBE COEFFICIENTS
Furthermore, the coefficient of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ and $\hat{\gamma}$; interestingly also on $\hat\lambda$ and $\hat{v}_{cal}$.
The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 
but has the extra factor $\lambda$ (range: 4--12), resulting in the products of coefficients and process variables being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$.
It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}). 
This negative correlation could hint a compenzation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
Similarly, signs of coefficients of $\lambda \cdot T_{cal}$ and $h(\lambda -6) \cdot T_{DB}$ correlate negatively in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) and the product of coefficients and input variables are again similar in order of magnitude. 
%It should be doubted, though, that the $layr$ only appears as interaction term 
%together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
%
%It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
%with $T_{cal}$ and $T_{DB}$. 
%From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_{DB}$ and then the rest of the independent variables. 
The process variables $T_{cal}$ and $\lambda$ appear as \gls{bf}s in generation 3 and 4, whereas $v_{cal}$ only appears in generation 3's \gls{rf}s and $T_{DB}$ only in generation 4's \gls{rf}s.
This can hint the importance of these variables in the process. 
%I highly doubt though that the specific interactions proposed by EMMA are indeed meaningful.

%%% MSE
For each generation the \gls{mse} was calculated for which only samples 
from the optimization were used which were available at the time of prediction. 
That means 15, 20, 25 and 30 samples 
%for $t=0$, 15 samples for $t=1$ and 30 samples for $t=4$ 
were used to calculate \gls{mse}s at $t=1,2,3,4$, respectively (compare with table~\ref{tab:emma-Gb}).
The \gls{mse}s are 64, 158, 54 and 50 for $t=1,2,3,4$, respectively. 
It is interesting that although prediction functions for $t=3$ predicted $v_{cal}$ perfectly, the combined \gls{mse} for $t=4$ is lower. 
The high \gls{mse} at $t=2$ can be explained by the prediction functions being only constant values. 
Apart from the second generation the \gls{mse} decreases  over time, 
which indicates that the algorithm works. 
This decrease in \gls{mse} might be attributed to overfitting, though, since prediction and validation were performed on the same data. 
%The \gls{mse} for each generation was also calculated between predicted values for pre-optimization samples to check for overfitting, 
The \gls{mse} for each generation's prediction function was also calculated for pre-optimization (out-of-sample) samples, which are unseen data. 
The error sank again with each generation (except for the second generation): 102, 118, 58, 50, respectively for $t=1,2,3,4$. 
%This shows 
The decrease of \gls{mse} with out-of-sample data shows that the regularization method 
of the \gls{mars} algorithm in principle works on investigated samples and that decrease of \gls{mse} is not due to overfitting. 
%
%\td{It should be noted, that the validation \gls{mse} for $t=1$ is much higher.}
When comparing the out-of-sample and in-sample \gls{mse}s it can be noted that at $t=1$ the out-of-sample \gls{mse} is close to 1.5 fold of in-sample and at $t=2$ vice versa.
%The high validation \gls{mse} for $t=1$ (nearly 1.5 fold instead of circa 1 fold of \gls{mse}) 
This shows the poor prediction ability at the beginning of the optimization which improved with generations.
This decrease in validation (out-of-sample) \gls{mse} supports the hypothesis stated at the beginning of this section: 
the measure of conductance was underestimated and the estimate improved over time (see table~\ref{tab:emma-pred-G}).
%\td{why is \gls{mse} higher with higher values? No homoscedasticity ( equality of variance)?
%Or rather \gls{mse} at $t=2$ high because \gls{rf}s at $t=2$ poor and gen=2 samples are chosen with help of \gls{rf} at $t=2$? 
%}

%%% PROBLEMS 
Even though the main \textit{optimizands} were minimized as required, the \gls{rf}s were not satisfactory. 
The two main problems were too many independent variables and too many dependent variables. 
Both seem closely related and overcomplicate the optimization, but both come with their own implications. 
Too many independent variables make it harder to distinguish variance due to random error (e.g. unmeasured and uncontrolled variables) from variance due to dependency. % of chosen dependent variables. 
The difficulty of identifying meaningful correlation is mainly owed to the curse of dimensionality\cite{friedman1988fitting} which makes it hard to collect enough data for each dimension. 
%
%In the here presented optimization model 
%the data points per independent variable 
%(events per predictor variable EPV) are as low as 5. 
The \gls{epv} (data points per independent varible) are as low as 5 in the here presented optimization. % model and data acquisition method
By eliminating three independent variables the \gls{epv} could rise to 10, which is stated 
as rule of thumb for multivariate regression\cite{vittinghoff2007relaxing}. 
The results obtained with limited sample number deliver remarkable insight %are quite respectable 
comparing to an \gls{epv} of 20-50 stated in the original \gls{mars} paper\cite{friedman1991multivariate} 
and an \gls{epv} of around 20 in the original \gls{emma} paper\cite{villanova2010function}. 
%In the original \gls{emma} paper\cite{villanova2010function} the \gls{epv} is 20.
%\td{In the original \gls{mars} paper\cite{friedman1991multivariate} the model is said 
%to work well on 20-50 events per predictor varibale.
%In the current model EPV are around 5, which is even low for a conservative 
%rule of thumbs of 10-15 EPV\cite{vittinghoff2007relaxing}.
%Not even rule of thumb of 10 EPV \cite{vittinghoff2007relaxing}
%Inspect \cite{friedman1988fitting,friedman1991multivariate} for further \gls{mars} discussion. 
%"The curse-of-dimensionality is fundamental and cannot be directly overcome."- Friedman 1988\cite{friedman1988fitting}.
%}
%

@@

The two independent variables $v_{cal}$ and $\lambda$ were included as \textit{optimizands} for two reasons: 
Maximizing the calcination velocity and minimizing the number of layer application iterations leads to minimization of process time.
The process time optimization would be better placed in a follow up study. 
The second reason for including independent variables was to check if the model works. 
This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimizands} and thus 
additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables and chose future data points. 
Moreover, $v_{cal}$ and $\lambda$ were only considered with 5\% weight. 
The second flaw is that there are obviously better methods to assess the quality of a model than to make it more complex. 
%Good alternatives would have been leave-one-out or cross validation.
Validation methods for sparse data include re-sampling via leave-one-out or $k$-fold cross validation\cite{kartam1997artificial}.

\iffalse
\td{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%\subsection{how did evolve over time?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{rational behind including $v_{cal}$ and $\lambda$ as optimizands}
}
%
%Three major flaws behind this consideration became obvious with time: 
%
\
\td{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations (\ref{eq:emma-G4})? And (\ref{eq:emma-phd4})?).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}

### 2023-05-14 doc/Thesis/chapter/062-post-emma.tex
delete unnecessary files and rearange folder structure

%
Finally, the \gls{mae} and \gls{mse} were calculated for different data sets 
(see table \ref{tab:post-emma}). 
Each models was trained on the \gls{emma} data set.
% EMMA 30 pts
The first two columns (e) show statistics validated with data the model was trained with (30 data points) and thus, 
these columns contain the lowest numbers. 
% pre-EMMA 21 pts 
The next two columns (p) were calculated with data obtained before the EMMA optimization (21 data points). 
As the pre-optimization data set was mainly used to find appropriate boundaries for the input variables, 
many data points are outside of the range of the \gls{emma} data set. 
Thus, prediction for this data set are mainly extrapolations. 
% inter/c/ pre-EMMA 5 pts
The next two columns (c) were produced by using pre-\gls{emma} data for validation, 
but only keeping points which sit inside the space spanned by the \gls{emma} constraints (5 data points). 
It should be expected that these statistics should be lower than in the previous two columns. 
They are only lower for MARS($\rho$) and LR($\rho$), though. 
This is likely due to the small sample size.
% all 51 
The last two columns show data for predictions of all available data (51 data points). 
These statistics are lower because of the inclusion of the training set in the test set.

In the self test of the first two columns \gls{mars} is the one method to rule them all and provides the lowest metrics.
But as soon as unseen data enters the field, linear regression excels by its simplicity. 
\td{The linear regression method is only under cut by \gls{svm} when calculating the \gls{mae} of $\gamma$}
for the interpolating unseen data (c).
%
%\todo{could use mean as prediction and compare}
%\todo{could plot pred vs true}
%\todo{pcr}
%\todo{step wise regression}
%\todo{why chose mae and mse}
%\todo{talk about sigma(pred) vs sigma(true)}
%\todo\url{https://blog.minitab.com/en/adventures-in-statistics-2/regression-smackdown-stepwise-versus-best-subsets}}
%\todo{\url{https://blog.minitab.com/en/how-to-choose-the-best-regression-model}}
%\todo{do regression for avg(-log(G)) instead of $\gamma$=avg( ( 13+log(G))**2)} 
%
\begin{table}[htb]
	\centering
%    \caption{Post EMMA vergleich}
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\gamma$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        LR&    13& 250&    24& 747&    34& 1327&   17& 454\\
%        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
        \hline
%    \hline\hline
	\end{tabular}
    %
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\rho$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        LR&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
%        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
%        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
        SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
    \hline\hline
	\end{tabular}
    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
	\label{tab:post-emma}
\end{table}

>>>>

%
Finally, the \gls{mae} and \gls{mse} were calculated for different data sets 
(see table \ref{tab:post-emma}). 
Each models was trained on the \gls{emma} data set.
% EMMA 30 pts
The first two columns (e) show statistics validated with data the model was trained with (30 data points) and thus, 
these columns contain the lowest numbers. 
% pre-EMMA 21 pts 
The next two columns (p) were calculated with data obtained before the EMMA optimization (21 data points). 
As the pre-optimization data set was mainly used to find appropriate boundaries for the input variables, 
many data points are outside of the range of the \gls{emma} data set. 
Thus, prediction for this data set are mainly extrapolations. 
It must be explicitly noted at this point that pre-EMMA samples differ from EMMA samples 
in the stabilization agent and therefore might underperform. 
% inter/c/ pre-EMMA 5 pts
The next two columns (c) were produced by using pre-\gls{emma} data for validation, 
but only keeping points which sit inside the space spanned by the \gls{emma} constraints (5 data points). 
It should be expected that these statistics should be lower than in the previous two columns. 
They are only lower for MARS($\rho$) and LR($\rho$), though. 
This is likely due to the small sample size.
% all 51 
The last two columns show data for predictions of all available data (51 data points). 
These statistics are lower because of the inclusion of the training set in the test set.

In the self test of the first two columns \gls{mars} is the one method to rule them all and provides the lowest metrics.
But as soon as unseen data is examined, linear regression excels by its simplicity. 
%\td{The linear regression method is only undercut by \gls{svm} when calculating 
%the \gls{mae} of $\gamma$} for the interpolating unseen data (c).
%
%\todo{could use mean as prediction and compare}
%\todo{could plot pred vs true}
%\todo{pcr}
%\todo{step wise regression}
%\todo{why chose mae and mse}
%\todo{talk about sigma(pred) vs sigma(true)}
%\todo\url{https://blog.minitab.com/en/adventures-in-statistics-2/regression-smackdown-stepwise-versus-best-subsets}}
%\todo{\url{https://blog.minitab.com/en/how-to-choose-the-best-regression-model}}
%\todo{do regression for avg(-log(G)) instead of $\gamma$=avg( ( 13+log(G))**2)} 
%
\begin{table}[htb]
	\centering
%    \caption{Post EMMA vergleich}
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\gamma$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        LR&    13& 250&    24& 747&    34& 1327&   17& 454\\
%        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
        \hline
%    \hline\hline
	\end{tabular}
    %
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\rho$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        LR&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
%        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
%        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
        SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
    \hline\hline
	\end{tabular}
    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
	\label{tab:post-emma}
\end{table}
